PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2022-06-03 main.tex

In section \ref{sec:theory} we provide an overview of the theory
behind planetesimal accretion and show that assumptions used to derive
the well-known modes of growth are only valid at sufficiently long
orbital periods. We then motivate the need for N-body simulations to
study this problem and describe the code used, along with how our
initial conditions were constructed in section \ref{sec:methods}. In
section \ref{sec:narrow}, we present a parameter study of planetesimal
accretion using a series of simulations of narrow annuli at various
orbital periods.  In section \ref{sec:fulldisk}, we present a set of simulations starting with a much wider planetesimal disk and demonstrate that a transition between accretion modes occurs at moderately small ($\simeq$ 50d) orbital periods. Next, we assess the impact of simplifications made to our collision model on this result in section \ref{sec:assump}. In section \ref{sec:discuss}, we discuss the implications of this multimodal accretion behavior throughout the disk for planet formation models and conclude.

@@

In the limit that $v_{esc} \gg v$, it can be shown that $M \propto
M^{4/3}$, which implies a runaway scenario, in which growth
accelerates with mass. This mode of growth was confirmed with N-body
simulations by \citet{kokubo96} and appears necessary to construct
protoplanets within the lifetime of a protoplanetary disk. Due to the
velocity dependence of the gravitational focusing effect, it is not clear how ubiquitous this mode of growth is. In particular, encounter velocities at short orbital periods will be rather large (because $v \sim v_{k}$) and the $v_{esc} \gg v$ condition may not always be satisfied. The effect that a dynamically hot disk has on runway growth will be examined in detail in section \ref{sec:results}.
%TRQ: fix section reference.

>>>>

In section \ref{sec:theory} we provide an overview of the theory behind planetesimal accretion and show that assumptions used to derive the well-known modes of growth are only valid at sufficiently long orbital periods. We then motivate the need for N-body simulations to study this problem and describe the code used, along with how our initial conditions were constructed in section \ref{sec:methods}. In section \ref{sec:narrow}, we present a parameter study of planetesimal accretion using a series of simulations of narrow annuli at various orbital periods. We also present a set of simulations starting with a much wider planetesimal disk and demonstrate that a transition between accretion modes occurs at moderately small ($\simeq$ 50d) orbital periods. Next, we assess the impact of simplifications made to our collision model on this result in section \ref{sec:assump}. In section \ref{sec:discuss}, we discuss the implications of this multimodal accretion behavior throughout the disk for planet formation models and conclude.

@@

In the limit that $v_{esc} \gg v$, it can be shown that $M \propto M^{4/3}$, which implies a runaway scenario, in which growth accelerates with mass. This mode of growth was confirmed with N-body simulations by \citet{kokubo96} and appears necessary to construct protoplanets within the lifetime of a protoplanetary disk. Due to the velocity dependence of the gravitational focusing effect, it isn't clear how ubiquitous this mode of growth is. In particular, encounter velocities at short orbital periods will be rather large (because $v \sim v_{k}$) and the $v_{esc} \gg v$ condition may not always be satisfied. The effect that a dynamically hot disk has on runway growth will be examined in detail in section \ref{sec:narrow}.
